Comparing OTU quality across clustering strategies

### 2021-10-30 exploratory/2021/algorithm-diagram_2021-08.Rmd

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph, title = '', 
                       is_last_plot = FALSE,
                       hide_loops = FALSE) {
  loop_dir <- ifelse(is_last_plot, 270, 90)
  loop_color <- ifelse(hide_loops, 'white', 'black')
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(span = 1, 
                     direction = loop_dir, 
                     strength = 0.2,
                     color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c(loop_color)
                            ) +
  labs(title = title) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

## do backend in python until the actual plotting step
```{python optifit}
import code.py.algorithm_diagram
optifit = create_optifit()
iters = optifit.iterate
dists = dist_sets_to_array(optifit.fitmap.dist_mat)
```
```{r pytor}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit <- create_optifit() 
dist_array <- optifit$fitmap$dists_to_array %>% py_to_r()
optifit_iters <- optifit$iterate %>% 
  lapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r() %>% 
                 mutate(is_loop = from == to)))
    })
```

@@

```{r plot_optifit_iters, fig.dim=c(6.875,6.875), dpi=300}
i <- 0
lapply(optifit_iters, function(x) {
  i <<- i + 1
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph(title = glue('{i}) mcc = {x$edges %>% filter(is_loop) %>% pull(mcc)}'),
               is_last_plot = i == length(optifit_iters),
               hide_loops = FALSE)
}) %>% 
  wrap_plots(ncol = 1)
```

>>>>

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph, title = '', 
                       hide_loops = FALSE) {
  loop_dir <- 90
  loop_color <- ifelse(hide_loops, 'white', 'black')
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(span = 1, 
                     direction = loop_dir, 
                     strength = 0.5,
                     color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c(loop_color)
                            ) +
  labs(title = title) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

## do backend in python until the actual plotting step
```{python dist_mat}
import pandas as pd
dist_mat = pd.DataFrame.from_dict({
    "seq1": ["D", "F", "G", "H", "I", "I", "J", "J", "N", "O", "P", "P", "P", "Q", "Q", 'X', 'X', 'X', 'X', 'Y', 'W', 'W', 'W'], 
    "seq2": ["B", "E", "C", "A", "B", "D", "A", "H", "M", "L", "K", "L", "O", "E", "F", 'Y', 'C', 'G', 'N', 'C', 'M', 'N', 'F']})
```
```{r optifit}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit <- create_optifit() 
#dist_array <- optifit$fitmap$dists_to_array %>% py_to_r()

optifit_iters <- optifit$iterate %>% 
  lapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r() %>% 
                  bind_rows(data.frame(from = 1, to = 1, mcc = NA)) %>% 
                 mutate(is_loop = from == to,
                        loop_dir = ifelse(from == 1, 270, 90))))
    })
```

@@

```{r plot_optifit_iters, fig.dim=c(6.875,6.875), dpi=300}
i <- 0
lapply(optifit_iters, function(x) {
  i <<- i + 1
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph(title = glue('{i}) mcc = {x$edges %>% filter(is_loop) %>% pull(mcc)}'),
               hide_loops = TRUE)
}) %>% 
  wrap_plots(ncol = 1)
```
